```{r import}
print(getwd())
#df = read.csv("./lib/competition/MemphisPopulation.csv")
population = read.csv("./lib/competition/MemphisPopulation.csv")
travel = read.csv("./lib/competition/MemphisTravel.csv")
dwellings = read.csv("./lib/competition/MemphisDwellings.csv")

#Merge the data by the common row field
df = merge(population, travel, by = "ZIP.code")

#Print all column names 
print(colnames(df))
```

```

```{r calculated_fields}

#Make a calculated field household_pop_density that is the ratio of population
#to households:
df$household_pop_density <- df$Population / df$Number.of.households

#proportion of vehicles per household (will assume all people can fit into the vehicle)
df$proportion_vehicle <- df$Households.with.1..vehicles.x / df$Number.of.households

#proportion of those who work (over age 16 and work)
df$proportion_work <- df$Population.age.16..years.old.who.work / df$Population

#proportion of those who work from home if they work
df$proportion_wfh <- df$Primary.mode.of.transportation.to.work..persons.aged.16.years....other.and.work.from.home / df$Population.age.16..years.old.who.work


```

